---
title: Income Inequality on Renewable Energy and SDGs
subtitle: Pathways Toward Achieving the Sustainable Development Goals (SDGs)
author:
  - name: Kayode Ogundare
    email: kazuharu.yanagimoto@cemfi.edu.es
    orcid: 0009-0007-1967-8304
    affiliations:
      - name: CEMFI
  - name: Victo Arowolo
    email: iamvictorthrive@gmail.com
abstract: |
  {{< lipsum 2 >}}
thanks: |
  You can write acknowledgements here.
keywords:
  - Quarto
  - Typst
  - format
date: today
date-format: full
bibliography: references.bib
format:
  academic-typst:
    section-numbering: "1.1.1"
execute:
  echo: false
  warning: false
---

This study examines economic (GDP, FDI, Trade, Labour), social (GINI, Urbanization), environmental (Renewable Energy Consumption, Carbon Emissions, Energy Intensity), and institutional (Regulatory Quality) variables to capture the multidimensional drivers of development. Together, these indicators provide a comprehensive framework for assessing the interactions between growth, inequality, sustainability, and governance.

## Variable Overview
| Category       | Short Form | Full Form                  | Source |
|----------------|------------|----------------------------|--------|
| Economic       | GDP        | Gross Domestic Product     | WDI    |
| Economic       | FDI        | Foreign Direct Investment  | WDI    |
| Economic       | TRADE      | Trade (% of GDP)           | WDI  |
| Economic       | LABOUR     | Labour Force Total         | WDI  |
| Social         | GINI       | Income Inequality (Gini Index)      | SWIID    |
| Social         | URBAN      | Urban Population (% of total) | WDI  |
| Environmental  | REC        | Renewable Energy Consumption         | WGI    |
| Environmental  | CARBON     | Carbon Dioxide Emissions | WDI  |
| Environmental  | ENERGY_INTENSITY | Energy Intensity (MJ per US$2015 GDP) | WDI  |
| Institutional  | REG_QUALITY| Regulatory Quality         | WGI    |


## Models 2
To provide robust insights into the relationship between income inequality, renewable energy consumption, and the SDGs, three econometric models are considered. The Autoregressive Distributed Lag (ARDL) model serves as the baseline framework, capturing both short-run adjustments and long-run equilibrium dynamics. The Pooled Mean Group (PMG-ARDL) model extends this by imposing homogeneity on the long-run coefficients across countries while allowing heterogeneity in the short-run dynamics. In contrast, the Mean Group (MG) model relaxes all homogeneity assumptions, estimating country-specific coefficients to account for structural differences across economies.

$$
\begin{equation}
Y_{it} = \alpha_i + \sum_{j=1}^{p} \phi_{ij} Y_{i,t-j} + \sum_{j=0}^{q} \beta_{ij} X_{i,t-j} + \varepsilon_{it}
\end{equation}
$$
$$
\begin{equation}
Y_{it} = \alpha_i + \lambda Y_{i,t-1} + \delta' X_{i,t} + \sum_{j=1}^{p-1} \phi_{ij} \Delta Y_{i,t-j} + \sum_{j=0}^{q-1} \theta_{ij} \Delta X_{i,t-j} + \varepsilon_{it}
\end{equation}
$$
$$
\begin{equation}
Y_{it} = \alpha_i + \lambda_i Y_{i,t-1} + \delta_i' X_{i,t} + \sum_{j=1}^{p-1} \phi_{ij} \Delta Y_{i,t-j} + \sum_{j=0}^{q-1} \theta_{ij} \Delta X_{i,t-j} + \varepsilon_{it}
\end{equation}
$$

## Descriptive statistics

```{r}

source("../02-analysis.R")
variable_summary
```


I don't use and don't recommend using heading levels 3 and below but it works.

## Citation

You can cite a reference like this [@katsushika1831] or @horst2020.
Typst has some built-in citation styles. Check the [Typst documentation](https://typst.app/docs/reference/model/bibliography/#parameters-style) for more information.

# Figures and Tables

## Figures

As @fig-hist-mpg shows, the caption is displayed below the figure.
As a caption of the figure (`fig-cap`), I use bold text for the title and use a normal text for the description.

```{r}
#| label: fig-hist-mpg
#| fig-cap: "**Histogram of Miles per Gallon**. The x-axis shows the miles per gallon, and the y-axis shows the frequency."

hist(mtcars$mpg)
```

## Tables

You can use [tinytable](https://vincentarelbundock.github.io/tinytable/)
for general tables and [modelsummary](https://vincentarelbundock.github.io/modelsummary/) for regression tables.^[Since the default backend of `modelsummary` is `tinytable`, you can use the customization options of `tinytable` for `modelsummary`.]
As @tbl-mtcars-head shows, the caption is displayed above the table.
The notes of the table can be added using the `notes` argument of the `tinytable::tt()` function.

```{r}
#| label: tbl-mtcars-head
#| tbl-cap: Head of the mtcars Dataset

nt <- "_Notes_: This table shows the first six rows of the mtcars dataset."
mtcars[1:5, 1:5] |>
  tinytable::tt(width = 0.8, notes = nt)         
```
# Last words

I made this template for my working papers, so it may not be suitable for other fields than economics.
I am happy to receive feedback and suggestions for improvement.

{{< appendix >}}

# Supplemental Figures

The figure numbering will be reset to "A.1", "A.2", etc so that it is clear that these figures are part of the appendix.

```{r}
#| label: fig-scatter-car
#| fig-cap: "**Scatter Plot of Car Data**. The x-axis shows the weight of the car, and the y-axis shows the miles per gallon."

plot(mtcars$wt, mtcars$mpg)
```

{{< pagebreak >}}
<!-- Bibliography -->
